\section*{General Information}
\textbf{Name:} Full Name \\
\textbf{Website:} None \\
\textbf{Location:} None \\
\textbf{Email:} None \\
\section*{Education}
\begin{itemize}
  \item \textbf{Computational Science, Engineering, and Mathematics PhD} (2023-)
    \textit{University of Texas at Austin}
  \item \textbf{Mathematics and Computer Science BSLAS; Highest Distinction} (2019-2023)
    \textit{University of Illinois at Urbana-Champaign}
\end{itemize}
\section*{Research Experience}
\begin{itemize}
  \item \textbf{Graduate Research Assistant} (2023-)
    \textit{University of Texas at Austin}
    \begin{itemize}
      \item \textbf{<b>Performance Portable Spectral Ewald Method for Stokes Flow</b>}
        \item Developed in PyKokkos for implementations on devices with shared memory and streaming parallelism (GPUs, APUs, etc.)
        \item Performance profiling with <b>Tau</b> <b>NSIGHT Compute</b> suite of tools for runs using NVIDIA’s A100 GPUs on the TACC Lonestar 6 supercomputer. These results are compared with cache aware pen-and-paper performance modeling.
        \item Invited to AMD tools workshop at the University of Oregon port the algorithm onto ROCM architecture and tune for performance on AMD Instinct™ series MI300A devices.
    \end{itemize}
  \item \textbf{Undergraduate Research - Department of Energy Science Undergraduate Laboratory Intern} (2022)
    \textit{National Renewable Energy Laboratory}
    \begin{itemize}
      \item Worked on Evaluating The Interplay Between Trajectory Segmentation and Mode Inference Errors
      \item \textbf{<b>Introduced a framework</b> to evaluate accuracy of trip length computations and mode inference for continuous mode-segmented trajectories on groups of trips}
        \item Developed a temporal alignment algorithm to classify temporal and spatial errors in a single metric and implemented the algorithm in python <a href="https://github.com/kennykos/mobilitynet-analysis-scripts/blob/pr_staging/classification_analysis.ipynb" target="_blank">https://github.com/kennykos/mobilitynet-analysis-scripts/blob/pr_staging/classification_analysis.ipynb</a>
        \item Applied the framework to the NREL OpenPATH pipeline using MobilityNet, a public dataset containing information from three artificial timelines that cover 15 different travel modes.
        \item Evaluated travel data collected on smartphones on android and iOS operating systems that was post-processed by different machine learning algorithms.
      \item <b>Results presented</b> at the <a href="https://www.trb.org/AnnualMeeting/AnnualMeeting.aspx" target-"_blank" </a>Transportation Research Board Annual Meeting 2023
    \end{itemize}
  \item \textbf{Undergraduate Researcher} (2022-2023)
    \textit{University of Illinois Urbana-Champaign}
    \begin{itemize}
      \item <b>Co-designed and Co-developed a dynamical model</b> with another undergraduate student and Professor Rapti to investigate Daphnia dentifera disease dynamics.
      \item <b>Presented results</b> at the University of Illinois Chicago Undergraduate Mathematics Symposium 2022 and the University of Illinois Urbana-Campaign Undergraduate Research Symposium 2022.
    \end{itemize}
  \item \textbf{Undergraduate Research - Illinois Geometry Lab} (2021-2022)
    \textit{University of Illinois Urbana-Champaign}
    \begin{itemize}
      \item \textbf{<b>Investigated packing capacities</b> with a team of undergraduate student and Professor Palmer to exactly compute packing capacities.}
        \item Developed an algorithm to explicitly compute toric packing capacities and implemented the algorithm in python <a href="https://github.com/CoulsonZhang/Semi-toric_Packing_Capacity" target="_blank">https://github.com/CoulsonZhang/Semi-toric_Packing_Capacity</a>.
        \item Solved the equivariant semitoric perfect packing problem.
      \item <a href="https://arxiv.org/abs/2210.06415" target="_blank">Co-authored a manuscript</a> currently in the journal submission process.
      \item <b>Presented results</b> at University of Illinois Urbana-Campaign Illinois Geometry Lab Poster Presentation Spring 2021, Fall 2022, Spring 2022.
      \item <b>Received</b> 2022 Illinois Geometry Lab Outstanding Research Award.
    \end{itemize}
\end{itemize}
\section*{Community Involvement}
\begin{itemize}
  \item \textbf{STEM Mentor} (2022)
    \begin{itemize}
      \item Assisted in the teaching of a data-science curriculum at Kenwood Academy high school in Chicago for 11th and 12th graders.
      \item Developed a plant biology and environmental sustainability curriculum for 2nd graders which will be taught at the Urbana Neighborhood Connections Center.
    \end{itemize}
  \item \textbf{Students for Environmental Concerns} (2020-2023)
    \textit{Secretary (August 2021-May 2022), President (August 2022-May 2023)}
    \begin{itemize}
      \item Lead an executive board of 10 undergraduates and an organization with 50+ general members.
      \item Oversee fundraising of $500+ per academic semester.
      \item \textbf{Develop and oversee various projects}
        \item Develop and teach curriculum regarding environmental ecology and sustainability to Urbana elementary school students.
        \item Work with Facilities and Services to implement a green-rooftop on the engineering campus.
        \item Run a community garden with a local non-profit.
        \item Generate and publish independent University of Illinois System Green Investment Report.
        \item Publish the Green Observer Environmental Magazine
        \item Implement Illinois Climate Action Plan objectives.
    \end{itemize}
  \item \textbf{Illinois Student Government} (2019-2022)
    \textit{Champaign County Board Liaison}
    \begin{itemize}
      \item Served as Quorum member for the Student Government Department of Governmental Relations.
      \item Attended Champaign County Board meetings and engaged in discussion with council members to build and maintain healthy relations between the Illinois Student Government and Champaign County.
      \item Co-authored resolutions regarding criminal justice
    \end{itemize}
\end{itemize}
\section*{Open Source Projects}
\begin{itemize}
  \item \textbf{<a href="https://toriis.earth">TORIIS</a>} (2023)
    \begin{itemize}
      \item B
      \item u
      \item i
      \item l
      \item d
      \item i
      \item n
      \item g
      \item  
      \item t
      \item h
      \item e
      \item  
      \item T
      \item r
      \item a
      \item n
      \item s
      \item p
      \item a
      \item r
      \item e
      \item n
      \item t
      \item  
      \item a
      \item n
      \item d
      \item  
      \item O
      \item p
      \item e
      \item n
      \item  
      \item R
      \item e
      \item s
      \item o
      \item u
      \item r
      \item c
      \item e
      \item  
      \item f
      \item o
      \item r
      \item  
      \item I
      \item n
      \item s
      \item t
      \item i
      \item t
      \item u
      \item t
      \item i
      \item o
      \item n
      \item a
      \item l
      \item  
      \item I
      \item n
      \item v
      \item e
      \item s
      \item t
      \item m
      \item e
      \item n
      \item t
      \item s
      \item  
      \item i
      \item n
      \item  
      \item c
      \item o
      \item l
      \item l
      \item a
      \item b
      \item o
      \item r
      \item a
      \item t
      \item i
      \item o
      \item n
      \item  
      \item w
      \item i
      \item t
      \item h
      \item  
      \item <
      \item a
      \item  
      \item h
      \item r
      \item e
      \item f
      \item =
      \item "
      \item h
      \item t
      \item t
      \item p
      \item s
      \item :
      \item /
      \item /
      \item u
      \item i
      \item u
      \item c
      \item .
      \item h
      \item a
      \item c
      \item k
      \item 4
      \item i
      \item m
      \item p
      \item a
      \item c
      \item t
      \item .
      \item o
      \item r
      \item g
      \item /
      \item "
      \item >
      \item H
      \item a
      \item c
      \item k
      \item 4
      \item I
      \item m
      \item p
      \item a
      \item c
      \item t
      \item  
      \item U
      \item I
      \item U
      \item C
      \item <
      \item /
      \item a
      \item >
      \item  
      \item a
      \item n
      \item d
      \item  
      \item <
      \item a
      \item  
      \item h
      \item r
      \item e
      \item f
      \item =
      \item "
      \item h
      \item t
      \item t
      \item p
      \item s
      \item :
      \item /
      \item /
      \item s
      \item e
      \item c
      \item s
      \item a
      \item t
      \item u
      \item i
      \item u
      \item c
      \item .
      \item w
      \item e
      \item b
      \item .
      \item i
      \item l
      \item l
      \item i
      \item n
      \item o
      \item i
      \item s
      \item .
      \item e
      \item d
      \item u
      \item /
      \item "
      \item >
      \item S
      \item t
      \item u
      \item d
      \item e
      \item n
      \item t
      \item s
      \item  
      \item f
      \item o
      \item r
      \item  
      \item E
      \item n
      \item v
      \item i
      \item r
      \item o
      \item n
      \item m
      \item e
      \item n
      \item t
      \item a
      \item l
      \item  
      \item C
      \item o
      \item n
      \item c
      \item e
      \item r
      \item n
      \item s
      \item <
      \item /
      \item a
      \item >
      \item .
    \end{itemize}
  \item \textbf{<a href="https://www.nrel.gov/transportation/openpath.html">NREL OpenPATH</a>} (2022)
    \begin{itemize}
      \item I
      \item m
      \item p
      \item l
      \item e
      \item m
      \item e
      \item n
      \item t
      \item e
      \item d
      \item  
      \item a
      \item  
      \item c
      \item o
      \item n
      \item t
      \item i
      \item n
      \item u
      \item o
      \item u
      \item s
      \item  
      \item m
      \item o
      \item d
      \item e
      \item -
      \item s
      \item e
      \item g
      \item m
      \item e
      \item n
      \item t
      \item e
      \item d
      \item  
      \item t
      \item r
      \item a
      \item j
      \item e
      \item c
      \item t
      \item o
      \item r
      \item y
      \item  
      \item <
      \item a
      \item  
      \item h
      \item r
      \item e
      \item f
      \item =
      \item "
      \item h
      \item t
      \item t
      \item p
      \item s
      \item :
      \item /
      \item /
      \item g
      \item i
      \item t
      \item h
      \item u
      \item b
      \item .
      \item c
      \item o
      \item m
      \item /
      \item k
      \item e
      \item n
      \item n
      \item y
      \item k
      \item o
      \item s
      \item /
      \item m
      \item o
      \item b
      \item i
      \item l
      \item i
      \item t
      \item y
      \item n
      \item e
      \item t
      \item -
      \item a
      \item n
      \item a
      \item l
      \item y
      \item s
      \item i
      \item s
      \item -
      \item s
      \item c
      \item r
      \item i
      \item p
      \item t
      \item s
      \item /
      \item b
      \item l
      \item o
      \item b
      \item /
      \item p
      \item r
      \item _
      \item s
      \item t
      \item a
      \item g
      \item i
      \item n
      \item g
      \item /
      \item c
      \item l
      \item a
      \item s
      \item s
      \item i
      \item f
      \item i
      \item c
      \item a
      \item t
      \item i
      \item o
      \item n
      \item _
      \item a
      \item n
      \item a
      \item l
      \item y
      \item s
      \item i
      \item s
      \item .
      \item i
      \item p
      \item y
      \item n
      \item b
      \item "
      \item  
      \item t
      \item a
      \item r
      \item g
      \item e
      \item t
      \item =
      \item "
      \item _
      \item b
      \item l
      \item a
      \item n
      \item k
      \item "
      \item >
      \item e
      \item v
      \item a
      \item l
      \item u
      \item a
      \item t
      \item i
      \item o
      \item n
      \item  
      \item f
      \item r
      \item a
      \item m
      \item e
      \item w
      \item o
      \item r
      \item k
      \item <
      \item /
      \item a
      \item >
      \item  
      \item t
      \item o
      \item  
      \item e
      \item v
      \item a
      \item l
      \item u
      \item a
      \item t
      \item e
      \item  
      \item t
      \item h
      \item e
      \item  
      \item N
      \item R
      \item E
      \item L
      \item  
      \item O
      \item p
      \item e
      \item n
      \item P
      \item A
      \item T
      \item H
      \item  
      \item p
      \item i
      \item p
      \item e
      \item l
      \item i
      \item n
      \item e
      \item .
    \end{itemize}
\end{itemize}
\section*{Honors and Awards}
\begin{itemize}
  \item \textbf{No Title} (2022)
\end{itemize}
